

\begin{thebibliography}{9}

\begin{enumerate}
\item M. Konishi,Associated production of top quarks with the Higgs boson at $\sqrt{s}$ =13 TeV. Paper presented at XXV International Workshop on Deep-Inelastic Scattering and Related Subjects, 3-7 April 2017, University of Birmingham, UK 

\item ATLAS, CMS Collaboration, Measurements of the Higgs boson production and decay rates and constraints on its couplings from a combined ATLAS and CMS analysis of the LHC pp collision data at $\sqrt s$ = 7 and 8 TeV, JHEP 08 (2016) 045 [arxiv:1606.02266]
 
\item The CMS Collaboration, Machine learning technique for signal-background separation of nuclear interaction vertices in the CMS detector,CMS-DP-2020-036 ; CERN-CMS-DP-2020-036


\item D. Bourilkov,Machine and Deep Learning Applications in Particle Physics,
[arxiv:1912.08245], \url{https://arxiv.org/pdf/1912.08245.pdf}

\item Y. LeCun, Y. Bengio and G. Hinton, Nature 521, 436 (2015). doi:10.1038/nature14539


\item D., Frédéric ; Peters, Y.et al.Top Quark Physics at the Tevatron, \url{https://ui.adsabs.harvard.edu/abs/2013IJMPA..2830013D}

\item J Mora :Thesis, Deep learning applied in the classification of events generated at the ATLAS experiment, \url{https://hdl.handle.net/11673/49967}


\item Ngairangbam, V.S., Bhardwaj, A., Konar, P. et al. Invisible Higgs search through vector boson fusion: a deep learning approach. Eur. Phys. J. C 80, 1055 (2020). https://doi.org/10.1140/epjc/s10052-020-08629-w

\item  K. Albertsson et al., Machine learning in high energy physics community white paper. J. Phys. Conf. Ser. 1085(2), 022008 (2018)

\item A. Radovic, M. Williams, D. Rousseau, M. Kagan, D. Bonacorsi,
A. Himmel, A. Aurisano, K. Terao, T. Wongjirad, Machine learning at the energy and intensity frontiers of particle physics. Nature
560(7716), 41–48 (2018)

\item P. Baldi, K. Bauer, C. Eng, P. Sadowski, D. Whiteson, Jet substructure classification in high-energy physics with deep neural
networks. Phys. Rev. D 93(9), 094034 (2016)

\item CMS Draft Analysis Note:CMS AN-21-105, Search of a Vector Like Quark T' $\longrightarrow$ tH in diphoton final state. \url{https://prsaha.web.cern.ch/prsaha/Tprime_analysis/AN-21-105_temp.pdf}

\item He, K., Ren, S., Sun, J., \& Zhang, X.Deep Residual Learning for Image Recognition (2016), CoRR, abs/1512.03385

\item G. Krintiras, ttH and tH production at 13 TeV(2017), Conference Report,CMS CR -2017/176: \url{ https://cdsweb.cern.ch/record/2272651/files/CR2017_176.pdf}


\item \url{https://cms.cern/detector}
\item \url{https://cms.cern/detector/bending-particles}
\item \url{https://cms.cern/detector/bending-particles}
\item \url{https://cms.cern/news/how-cms-detects-particles}
\item \url{https://cms.cern/detector/identifying-tracks/silicon-strips}
\item \url{https://cms.cern/detector/computing-grid}
\item \url{https://machinelearningmastery.com/}
\item \url{https://keras.io/}
\item \url{https://towardsdatascience.com/}
\item \url{https://www.thomasgmccarthy.com/an-introduction-to-collider-physics-ix}
\item \url{https://openlearninglibrary.mit.edu/courses/course-v1:MITx+6.036+1T2019/courseware/Week7/neural_networks_2/}
\item \url{https://www.phys.ufl.edu/~avery/ivdgl/itr2001/proposal_all.pdf}
\item \url{https://edusera.org/machine-learning/}
\item \url{https://www.displayr.com/what-is-correlation/}

\item Guest D., Cranmer K.,Whiteson D., Deep Learning and Its Application to LHC Physics,Annu. Rev. Nucl. Part. Sci. 2018. \url{https://doi.org/10.1146/annurev-nucl101917-021019}


\item The CMS Collaboration, Machine learning technique for signal-background separation of nuclear interaction vertices in the CMS detector, CMS Performance Note(2020),CMS DP -2020/036
% \item G. Reuter, personal communication. [Must be accompanied with a letter of permission and must not be used to support a central claim, result, or conclusion.]
\end{enumerate}

\end{thebibliography}


















